A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2017-07-11 meth.tex
finish meth comments, update notebook for luc/non thresholds

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{decision_tree.png}
    \caption[]{
      \label{fig:decision_tree}
      The default method decision tree used in the \code{aneris} software
% * <maarten.vandenberg@pbl.nl> 2017-07-03T21:40:43.868Z:
% 
% > The default method decision tree
% yes and no might be added to the tree for improved clarity. 
% 
% ^.
      library. For all decisions, upper branches represent a ``yes'' response
      and lower branches represent a ``no'' response. $dH$ is defined as
      $\left|\frac{h(t_i) - m(t_i)}{h(t_i)}\right|$, and decision-making
      thresholds are described below. Methods labeled in \textit{green}
% * <maarten.vandenberg@pbl.nl> 2017-07-03T21:42:35.965Z:
% 
% for CoV and dH
% 
% ^.
      are likely closely match unharmonized results, methods
      in \textit{yellow} will likely somewhat match unharmonized results, and
      methods in \textit{red} can be expected to have a large relative
      difference between harmonized and unharmonized results.}
  \end{center}
\end{figure}

@@

The value of $c_v$ is then tested against a threshold. To determine this
threshold, an analysis of the recent CEDS and LUC historical data has been
performed. Figure \ref{fig:cov} shows the distribution of LUC $c_v$s and non-LUC
$c_v$s as determined for historical data aggregated to the model regions of 5
different IAMs \TODO{list here or elsewhere?}. A threshold value of 20 has been chosen based on these
observations as it optimally divides the two distributions. Importantly, tails
of the LUC and non-LUC overlap, thus there are both false positives (~10\% of
non-LUC trajectories) and false negatives (~7\% of LUC trajectories). However,
% * <maarten.vandenberg@pbl.nl> 2017-07-03T22:07:21.157Z:
% 
% >  (~10\% of
% > non-LUC trajectories) and false negatives (~7\% of LUC trajectories)
% visually it seems to be that the false negatives are a larger share thatn the false positives?
% 
% ^.
as any regional definition is model dependent and thus any regional aggregation
is possible an automated detection mechanism is necessary.

>>>>

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{decision_tree.png}
    \caption[]{
      \label{fig:decision_tree}
      The default method decision tree used in the \code{aneris} software
% * <maarten.vandenberg@pbl.nl> 2017-07-03T21:40:43.868Z:
% 
% > The default method decision tree
% yes and no might be added to the tree for improved clarity. 
% 
% ^.
      library. For all decisions, upper branches represent a ``yes'' response
      and lower branches represent a ``no'' response. $dH$ is defined as
      $\left|\frac{h(t_i) - m(t_i)}{h(t_i)}\right|$, and decision-making
      thresholds for $c_v$ and $dH$ are described below. Methods labeled in
      \textit{green} are likely to closely match unharmonized results, methods
      in \textit{yellow} will likely somewhat match unharmonized results, and
      methods in \textit{red} can be expected to have a large relative
      difference between harmonized and unharmonized results.}
  \end{center}
\end{figure}

@@

The value of $c_v$ is then tested against a threshold. To determine this
threshold, an analysis of the recent CEDS and LUC historical data has been
performed. Figure \ref{fig:cov} shows the distribution of LUC $c_v$s and non-LUC
$c_v$s as determined for historical data aggregated to the model regions of 5
different IAMs involved in the SSP process. A threshold value of 20 has been
chosen based on these observations as it optimally divides the two
distributions. Importantly, tails of the LUC and non-LUC overlap, thus there are
both false positives (~7\% of non-LUC trajectories) and false negatives (~10\%
of LUC trajectories). However, as any regional definition is model dependent and
thus any regional aggregation is possible an automated detection mechanism is
necessary.
